### 2017-03-02 IROS17/theory2robAlgs.tex
epsilon!
Added epsilon to caption

Assume two robots are initialized at $r_1$ and $r_2$ with corresponding goal destinations $g_1$ and $g_2$. 
The solution is a best-first search algorithm that maintains a list of possible paths ($moves$), sorted according to an admissible heuristic on path length.
The algorithm works by expanding the path with the shortest estimated length.
Expanding a path means either moving directly to the goal, or pushing one robot to a wall and adjusting the relative position of the other robot.
As soon as the goal is reached, the algorithm returns this shortest path.

@@

\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:optimalAlg}: two robot positioning using walls with infinite friction. 
Robot start positions are shown by a square, and goal positions by a circle.  Dashed lines show the shortest route if robots could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:optimalAlg}.
Online demonstration and source code at \cite{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}
\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the robots. Each robot gets the same control input. 
(left) If robot 2 hits the bottom wall before robot 1 reaches a wall, robot 2 can reach anywhere along the green line, and  robot 1 can move to anywhere in the shaded area. 
(right) Similarly, if robot 2 hits the right wall before robot 1 reaches a wall, robot 2 can reach anywhere along the green line, and  robot 1 can move to anywhere in the shaded area. 
} \vspace{-1em}
\end{figure}
If  $\Delta g$ is not in the reachable set, we choose the nearest reachable $\Delta x$ and $\Delta y$ to $\Delta g$. 
%For simplicity in this step, we choose the straight line from the touching robot to the wall for the first move. This may cause the algorithm not to return the shortest path, but the difference is not significant.

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.5\columnwidth}
{\begin{overpic}[width =\figwid]{epsilonMin.pdf}%\put(20,20){$\epsilon = 0.001$}
\put(20, 3.1){{\scriptsize$\swarrow$}~$\epsilon = 0.001$}
\end{overpic}
\begin{overpic}[width =\figwid]{epsilonMed.pdf}%\put(20,20){$\epsilon = 0.05$}
\put(20, 4){{\scriptsize$\updownarrow$}~$\epsilon = 0.05$}
\end{overpic}
\begin{overpic}[width =\figwid]{epsilonMax.pdf}%\put(20,20){$\epsilon = 0.1$}
\put(20, 5){{\Large$\updownarrow$}~$\epsilon = 0.1$}
\end{overpic}
}\\
\caption{\label{fig:epsilon}{Changing the minimum spacing $\epsilon$ changes the path.   $\epsilon$ is the minimum spacing between two robots and the minimum separation from the boundaries.}
\vspace{-1em}
}
\end{figure*}

@@

\vspace{1em}
\begin{overpic}[width =\figwid]{contourPlotNum.pdf}\put(97.5,21){7}
\put(97.5,18.5){6}
\put(97.5,16){5}
\put(97.5,13.5){4}
\put(97.5,11){3}
\end{overpic}
}\\
\caption{\label{fig:contourPlots}{Starting positions of robots $1$ and $2$ and goal position of robot $2$ are fixed, and 
 the top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The bottom row shows the number of moves required for the same configurations.}
\vspace{-1em}
}
\end{figure*}

>>>>

@@

\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:optimalAlg}: two robot positioning using walls with infinite friction. 
Robot start positions are shown by a square, and goal positions by a circle.  Dashed lines show the shortest route if robots could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:optimalAlg}.
Online demonstration and source code at \cite{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
\vspace{-1em}
}
\end{figure*}
Assume two robots are initialized at $r_1$ and $r_2$ with corresponding goal destinations $g_1$ and $g_2$. 
The solution is a best-first search algorithm that maintains a list of possible paths ($moves$), sorted according to an admissible heuristic on path length.
The algorithm works by expanding the path with the shortest estimated length.
Expanding a path means either moving directly to the goal, or pushing one robot to a wall and adjusting the relative position of the other robot.
As soon as the goal is reached, the algorithm returns this shortest path.

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the robots. Each robot gets the same control input. 
(left) If robot 2 hits the bottom wall before robot 1 reaches a wall, robot 2 can reach anywhere along the green line, and  robot 1 can move to anywhere in the shaded area. 
(right) Similarly, if robot 2 hits the right wall before robot 1 reaches a wall, robot 2 can reach anywhere along the green line, and  robot 1 can move to anywhere in the shaded area. 
}
\end{figure}
If  $\Delta g$ is not in the reachable set, we choose the nearest reachable $\Delta x$ and $\Delta y$ to $\Delta g$. 
%For simplicity in this step, we choose the straight line from the touching robot to the wall for the first move. This may cause the algorithm not to return the shortest path, but the difference is not significant.

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.5\columnwidth}
{\begin{overpic}[width =\figwid]{epsilonMin.pdf}%\put(20,20){$\epsilon = 0.001$}
\put(20, 3.1){{\scriptsize$\swarrow$}~$\epsilon = 0.001$}
\end{overpic}
\begin{overpic}[width =\figwid]{epsilonMed.pdf}%\put(20,20){$\epsilon = 0.05$}
\put(20, 3.9){{\tiny$\updownarrow$}~$\epsilon = 0.05$}
\end{overpic}
\begin{overpic}[width =\figwid]{epsilonMax.pdf}%\put(20,20){$\epsilon = 0.1$}
\put(20, 5){{\large$\updownarrow$}~$\epsilon = 0.1$}
\end{overpic}
}\\
\caption{\label{fig:epsilon}{Changing the minimum spacing $\epsilon$ changes the path.   $\epsilon$ is the minimum spacing between two robots and the minimum separation from the boundaries.}
\vspace{-1em}
}
\end{figure*}

@@

\vspace{1em}
\begin{overpic}[width =\figwid]{contourPlotNum.pdf}\put(97.5,21){7}
\put(97.5,18.5){6}
\put(97.5,16){5}
\put(97.5,13.5){4}
\put(97.5,11){3}
\end{overpic}
}\\
\caption{\label{fig:contourPlots}{Starting positions of robots $1$ and $2$ and goal position of robot $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The bottom row shows the number of moves required for the same configurations.}
\vspace{-1em}
}
\end{figure*}
